\documentclass[a4paper,9.5pt]{article}
\usepackage{geometry}
\geometry{
  left=0.5in,
  right=0.5in,
  top=0.3in,
  bottom=0.3in
}
% \usepackage{helvet}
% \renewcommand{\familydefault}{\sfdefault}
\usepackage[sfdefault]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}

\usepackage[dvipsnames]{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{xhfill}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  filecolor=magenta,      
  urlcolor=cyan,
}
\urlstyle{same}

% \author{Ahmed Shariff}
\usepackage{multicol}
\title{}
\date{}
% \makeatletter
% \renewcommand{\@maketitle}{
%   \newpage
%   % \null
%   \vskip 2em%
%   \begin{center}%
%     {\LARGE \@title \par}%
%   \end{center}%
%   \par} \makeatother

\usepackage[
backend=biber,
style=ieee,
sorting=none
]{biblatex}
\usepackage{float}
% \floatstyle{boxed} 
\restylefloat{figure}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage[labelfont=it, font=small]{caption}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{tabulary}
\usepackage{array}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage{eso-pic}
\usepackage{fontawesome5}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{nopageno}
\addbibresource{citations.bib}
% \interfootnotelinepenalty=10000
% \numberwithin{figure}{section}
\newcommand{\fiverate}{{\footnotesize\color{Emerald}\faCircle\faCircle\faCircle\faCircle\faCircle}}
\newcommand{\fourrate}{{\footnotesize\color{Emerald}\faCircle\faCircle\faCircle\faCircle\faCircle[regular]}}
\newcommand{\threerate}{{\footnotesize\color{Emerald}\faCircle\faCircle\faCircle\faCircle[regular]\faCircle[regular]}}
\newcommand{\tworate}{{\footnotesize\color{Emerald}\faCircle\faCircle\faCircle[regular]\faCircle[regular]\faCircle[regular]}}
\newcommand{\drawratebox}[2]{%
  \makebox[0.4\textwidth]{~~#1\hfill#2~~}}
% from https://tex.stackexchange.com/questions/77821/insert-text-into-hrulefill
\newcommand*{\titlerulefill}[3][]{%
  \makebox[#2]{#1%
    \leaders\hrule height \dimexpr.5ex+.2pt\relax depth \dimexpr -.5ex+.2pt\relax \hfill% Left rule
    \enskip{#3}\enskip% Text (and surrounding spaces)
    \leaders\hrule height \dimexpr.5ex+.2pt\relax depth \dimexpr -.5ex+.2pt\relax \hfill\kern0pt}% Right rule
}
\newcommand{\skilltitle}[1]{\hfil\titlerulefill[\color{black!25}]{0.6\linewidth}{\footnotesize\color{black!45}#1}\hfil}
\newcommand{\sectiontitle}[1]{{\hfill\titlerulefill{0.7\textwidth}{\large #1}\hfill}\vspace{-0.5cm}}
\newcommand{\timeline}[3]{%
  \begin{tabbing}
    \=\hspace*{1cm}\=\hspace*{6cm}\=\hspace*{5cm}\= \kill
    \>\>\textbf{#1} \> \textbf{#2}\\\>\>\> \emph{#3}
  \end{tabbing}
}

\setlist[itemize]{leftmargin=2em}

\begin{document}
% \rule{\textwidth}{1pt}
% \vspace{0.45cm}
\begin{center}
  {\fontfamily{epigrafica}\selectfont\color{black!85}\LARGE \textbf{Shariff Faleel}}\\
\end{center}
\vspace{-0.4cm}
% \rule{\textwidth}{1pt}
% \begin{flushright}
\begin{center}
  Full name: \textbf{Ahmed Shariff Mohommed Faleel}\\[0.3cm]
  \textbullet~~\faIcon{mobile-alt} +14313746743~~\textbullet~~\faIcon{envelope}~shariff.mfa@outlook.com~~\textbullet~~\faIcon{link}~\url{shariff-faleel.com}~~\textbullet\\
  \textbullet~~\faIcon{github}~\url{github.com/ahmed-shariff}~~\textbullet~~\faIcon{linkedin}~\url{lk.linkedin.com/in/ahshariff}~~\textbullet
\end{center}
\sectiontitle{Summary}\\[0.1cm]
\begin{center}
  \parbox{0.9\linewidth}{Primary research interest is in augmenting human cognition. I
    am particularly interested in using state-of-the-art artificial
    intelligence technologies with ubiquitous computing to expand the
    human day-to-day experience. }
\end{center}
\vspace{0.1cm}
\input{technical_skills.tex}
% \rule{0.75\textwidth}{0.4pt}
% \\    
\vspace{0.4cm}
\sectiontitle{Work \& Research Experience}\\[3pt]
\begin{center}
  \begin{minipage}[h]{0.95\linewidth}
    \timeline{March 2021 - April 2022}{Associate Researcher, Intern}{Huawei Technologies Canada}
    \centering
    \vspace{-0.3cm}
    \begin{itemize}
      \setlength\itemsep{-0.1cm}
    \item Was part of the Human Machine Interactions lab. Worked on a range of HCI projects.
    \item Developed research ideas, executed relevant user studies and built demo applications.
    \item Produced a paper on typing on virtual keyboards (Accepcted at CHI '23).
    \end{itemize}
  \end{minipage}
\end{center}
\vspace{-0.1cm}
\begin{center}
  \begin{minipage}[h]{0.95\linewidth}
    \timeline{August 2019 - Present}{PhD Candidate}{University of British Columbia - Okanagan}
    \centering
    \vspace{-0.3cm}
    \begin{itemize}
      \setlength\itemsep{-0.1cm}
    \item Under the supervision of Prof. Pourang Irani.
    \item Exploring AR/VR input and output capabilities. Developed Hand Proximate UI as a novel interaction modality for AR/VR.
      \vspace{-5pt}
      \begin{itemize}
      \item Technologies Explored: Deep learning models (CV), Gesture-based interactions (Leap Motion, Vicon motion tracking, CV), VR/AR (Oculus, Epson \& Hololens using Unity, Android \& Python)
      \end{itemize}
      \vspace{-0.2cm}
    \item Was instructor for a graduate level course on introducing designing immersive applications for VR \& AR.
    \end{itemize}
  \end{minipage}
\end{center}
\vspace{-0.1cm}
\begin{center}
  \begin{minipage}[h]{0.95\linewidth}
    \timeline{July 2017 - August 2019}{Research Assistant}{University of Peradeniya}
    \centering
    \vspace{-0.3cm}
    \begin{itemize}
      \setlength\itemsep{-0.1cm}
    \item Under the supervision of Dr. R.D. Nawarathna.
    \item Conducted research on deep-learning based computer vision applications as part of a collaboration with codegen international.
    \item Developed a prototype system for a cashier assistant:
      \vspace{-5pt}
      \begin{itemize}
        \setlength\itemsep{-0.1cm}
      \item Tools/framworks used: NVIDIA Jetson, Raspberry Pi, Python, pytorch, django, AWS Lambda, AWS Beanstalk, MongoDB.
      \item Framework developed for automated ML experimenting, training and deployment.
      \end{itemize}
    \end{itemize}
  \end{minipage}
\end{center}
\vspace{-0.1cm}
\begin{center}
  \begin{minipage}[h]{0.95\linewidth}
    \timeline{March 2017 - June 2017}{Temporary Demonstrator}{University of Peradeniya}
    \centering
    \vspace{-0.3cm}
    \begin{itemize}
      \setlength\itemsep{-0.1cm}
    \item Conducted practical sessions (Programming concepts, Data structures and algorithms, Computer architecture/assembly) for undergraduate students. % The Medium of Instruction was English.
    \item Technical committee member of the Postgraduate Institute of Science Research Congress, 2017.
    \item Researched Dialogue Management systems.
    \end{itemize}
  \end{minipage}
\end{center}
\vspace{-0.1cm}
\begin{center}
  \begin{minipage}[h]{0.95\linewidth}
    \timeline{August 2016 - January 2016}{Software Engineering Intern}{IFS R\&D International}
    \centering
    \vspace{-0.3cm}
    \begin{itemize}
      \setlength\itemsep{-0.1cm}
    \item Developed dependency visualization of system modules. Using Common Lisp, Python, and Javascript.
    \end{itemize}
  \end{minipage}
\end{center}
\vspace{0.3cm}
\sectiontitle{Education}\\
\vspace{-0.4cm}\\
\begin{center}
  \begin{minipage}[h]{0.95\linewidth}
    \timeline{September 2019 - Present}{PhD (Computer Science)}{University of Britsh Columbia - Okanagan}
    \centering
    \vspace{-0.3cm}
    \textbullet~Supervisor - Prof. Pourang Irani \qquad \textbullet~GPA: 4.25/4.5
  \end{minipage}
\end{center}
\begin{center}
  \begin{minipage}[h]{0.95\linewidth}
    \timeline{March 2013 - December 2016}{BSc (Computer Science)}{University of Peradeniya}
    \centering
    \vspace{-0.3cm}
    \textbullet~Major: Computer Science \qquad \textbullet~Minor: Statistics \& Mathematics\\
    \textbullet~GPA: 3.5/4.0 (87\%) (Second Class Honours - Upper Division)
  \end{minipage}
\end{center}
\vspace{0.3cm}
\sectiontitle{Publications}
\vspace{0.1cm}\\
\begin{itemize}
  \item[]Francisco Perella-Holfeld, \textbf{Shariff AM Faleel}, Pourang Irani. (2023) ``Evaluating design guidelines for hand proximate in-situ user interfaces''. (In submission at DIS 2023)
  \item[]Fouad Alallah, \textbf{Shariff AM Faleel}, Yumiko Sakamoto, Bradley Rey, and Pourang Irani. (2023) ``Evaluation of Situated Space-time Cube Analytics for In-situ Data Exploration''. (In submission at Information Visualization)
  \item[]\textbf{Shariff AM Faleel}, Yishuo Liu, Roya A Cody, Bradley Rey, Linghao Du, Jiangyue Yu, Da-Yuan Huang, Pourang Irani, Wei Li. (2023) ``T-Force: Exploring the Use of Typing Force for Three State Virtual Keyboards''. (Accepted at CHI 2023)
  \item[]Ali Neshati, Aaron Salo, \textbf{Shariff AM Faleel}, Ziming Li, Hai-Ning Liang, Celine Latulipe, and Pourang Irani. 2022. ``EdgeSelect: Smartwatch Data Interaction with Minimal Screen Occlusion.'' In Proceedings of the 2022 International Conference on Multimodal Interaction (ICMI '22). Association for Computing Machinery, New York, NY, USA, 288–298. https://doi.org/10.1145/3536221.3556586
  \item[]Fouad Alallah, \textbf{Shariff AM Faleel}, Yumiko Sakamoto, Bradley Rey, and Pourang Irani (2022). ``SSCA: situated space-time cube analytics.'' In M. Agus, W. Aigner, and T. Hoellt, EuroVis 2022 - Short Papers (pp. ). : The Eurographics Association. https://doi.org/10.2312/evs.20221088
  \item[]\textbf{Shariff AM Faleel}, Michael Gammon, Kevin Fan, Da-Yuan Huang, Wei Li and Pourang Irani, ``HPUI: Hand Proximate User Interfaces for One-Handed Interactions on Head Mounted Displays,'' in IEEE Transactions on Visualization and Computer Graphics, vol. 27, no. 11, pp. 4215-4225, Nov. 2021, https://doi.org/10.1109/TVCG.2021.3106493.
  \item[]\textbf{Shariff AM Faleel}, Bibhushan Raj Joshi and Bradley Rey, ``Writely: Force Feedback for Non-Dominant Hand Writing Training,'' 2021 IEEE World Haptics Conference (WHC), 2021, pp. 340-340, https://doi.org/10.1109/WHC49131.2021.9517209.
  \item[]Ali Neshati, Bradley Rey, \textbf{Ahmed Shariff Mohommed Faleel}, Sandra Bardot, Celine Latulipe, and Pourang Irani. 2021. ``BezelGlide: Interacting with Graphs on Smartwatches with Minimal Screen Occlusion''. In Proceedings of the 2021 CHI Conference on Human Factors in Computing Systems (CHI '21). Association for Computing Machinery, New York, NY, USA, Article 501, 1–13. https://doi.org/10.1145/3411764.3445201
  \item[]\textbf{Shariff A. M. Faleel}, Michael Gammon, Yumiko Sakamoto, Carlo Menon, and Pourang Irani. 2020. ``User gesture elicitation of common smartphone tasks for hand proximate user interfaces''. In \textit{Proceedings of the 11th Augmented Human International Conference (AH '20)}. Association for Computing Machinery, New York, NY, USA, Article 6, 1–8. \\https://doi.org/10.1145/3396339.3396363
  \item[]Yurii Vasylkiv, Ali Neshati, \textbf{Shariff A. M. Faleel}, Yumiko Sakamoto, and Pourang Irani. 2020. ``Using guessability framework: age-related differences in hand gesture interaction''. In \textit{Proceedings of the 11th Augmented Human International Conference (AH '20)}. ACM, New York, NY, USA, Article 24, 1–2. https://doi.org/10.1145/3396339.3396394
  \item[]\textbf{Ahmed Shariff, M.F.}, Nawarathna, R.D. (2019). ``A Novel Dialogue Manager Model for Spoken Dialogue Systems Based on User Input Learning.'' In: Hemanth, J., Silva, T., Karunananda, A. (eds) Artificial Intelligence. SLAAI-ICAI 2018. Communications in Computer and Information Science, vol 890. Springer, Singapore. https://doi.org/10.1007/978-981-13-9129-3\_14
  \item[]\textbf{M.F.A. Shariff}. and R.D. Nawarathna, ``A Dialogue Management Model with User Input Learning.'' Proceedings of the Postgraduate Institute of Science Research Congress 2017. (Abstract)
\end{itemize}


% \vspace{15pt}
% \noindent\textbf{\large\textbar{Research Experience:}}
% \vspace{-8pt}\noindent\\\rule{0.75\textwidth}{0.4pt}
% \begin{itemize}
%   \setlength\itemsep{0pt}
% \item As part of the undergraduate course requirement, I presented a thesis report of the research project, in which I developed a model for a dialogue manager with tighter integration of the backend and user input learning. Also while working as a temporary demonstrator at the University of Peradeniya, I conducted research on dialogue management and machine learning, an extension of my final year research project.
% \item Currently I am employed as a research assistant, where I conduct research on computer vision and deep learning applications. The research project’s current focus is to build a system to automate billing in a restaurant, with computer vision as the primary method. Also we are using the Nvidia Jetson platform as the deployment device, and are experimenting with a wide range of deep learning algorithms and architectures.
% \end{itemize}

% \pagebreak
% \noindent\textbf{\large\textbar{References:}}
% \vspace{-8pt}\noindent\\\rule{0.75\textwidth}{0.4pt}\\
% \textbf{Dr. Amalka Pinidiyaarachchi, Ph.D. (Uppsala University, Sweden)},\\
% Senior Lecturer,\\
% Head / Department of Statistics and Computer Science,\\
% Faculty of Science,\\
% University of Peradeniya\\
% Peradeniya (20400),\\
% Sri Lanka.\\
% Email: 		ajp@pdn.ac.lk\\

% \noindent\textbf{Dr. Ruwan D. Nawarathna, Ph.D. (University of North Texas, USA)},\\
% Senior Lecturer,\\
% Department of Statistics and Computer Science,\\
% Faculty of Science,\\
% University of Peradeniya,\\
% Peradeniya (20400),\\
% Sri Lanka.\\
% Email: 		ruwand@pdn.ac.lk\\
% ruwan.nawarathna@gmail.com\\

% \noindent\textbf{Prof. Roshan D. Yapa, D.Eng. (Hiroshima University, Japan)},\\
% Professor in Statistics and Computer Science,\\
% Department of Statistics and Computer Science,\\
% Director / Science Industry Interaction Cell,\\
% Faculty of Science,\\
% University of Peradeniya,\\
% Peradeniya (20400),\\
% Sri Lanka.\\
% Email: 		roshany@pdn.ac.lk
% % ruwan.nawarathna@gmail.com\\


\end{document}